---
title: "24 Hour Fitness Clubs and Mobile/Pharmacy Clinics"
author: "Brandyn Ruiz"
output: html_document
---

```{r warning=FALSE, message=FALSE, echo=FALSE}
library(readr)
library(dplyr)
library(stringr)
library(lubridate)
library(ggplot2)
library(ggmap)
library(leaflet)
library(leaflet.extras2)
library(htmltools)
library(plotly)
library(kableExtra)
library(tidyverse)
```

```{r Compton Mobile Dataset, message=FALSE, echo=FALSE, warning=FALSE}
ComptonMobile <- read_csv("ComptonMobile.csv")

```

```{r echo=FALSE}
register_google(key = 'AIzaSyDq5iF4Ivj7nBQEFIxqBy06EkA5ACRTZgU')
```

```{r warning=FALSE, message=FALSE, echo=FALSE}
for (i in 1:nrow(ComptonMobile)){

  result <- geocode(ComptonMobile$Address[i], output = 'latlona', source = 'google')
  
  ComptonMobile$lon[i] <- as.numeric(result[1])
  ComptonMobile$lat[i] <- as.numeric(result[2])
  ComptonMobile$geoAddress[i] <- as.character(result[3])
}

write.csv(ComptonMobile, 'ComptonMobileGeo.csv')
```

```{r Compton Mobile Map, warning=FALSE, message=FALSE, echo=FALSE, include=FALSE}
leaflet(ComptonMobile)%>%
  addTiles()%>%
  addMarkers(~lon, ~lat, label = ~as.character(`Name of Facility`))
```

```{r Compton Pharmacy, warning=FALSE, message=FALSE, echo=FALSE}
ComptonPharmacy <- read_csv('ComptonPharmacy.csv')

ComptonPharmacy <- ComptonPharmacy%>%
  mutate(Pharmacy = str_extract(ComptonPharmacy$Name, '.*#'))%>%
  select(Pharmacy, Name, Address, Hours, `Type of Vaccine`, `Contact Number`)

ComptonPharmacy$Pharmacy <- sub(' #', '', ComptonPharmacy$Pharmacy)
```

```{r Compton Pharmacy Geo, warning=FALSE, message=FALSE, echo=FALSE}
for (i in 1:nrow(ComptonPharmacy)){

  result <- geocode(ComptonPharmacy$Address[i], output = 'latlona', source = 'google')
  
  ComptonPharmacy$lon[i] <- as.numeric(result[1])
  ComptonPharmacy$lat[i] <- as.numeric(result[2])
  ComptonPharmacy$geoAddress[i] <- as.character(result[3])
}

write.csv(ComptonPharmacy, 'ComptonPharmacyGeo.csv')
```

```{r Compton Mobile & Pharm, warning=FALSE, message=FALSE, echo=FALSE, include = FALSE}
leaflet(ComptonMobile)%>%
  addTiles()%>%
  addMarkers(~lon, ~lat, label = ~as.character(`Name of Facility`))%>%
  addMarkers(~lon, ~lat, label = ~as.character(Name), data = ComptonPharmacy)
```

```{r Lancaster Pharmacy, message=FALSE, warning=FALSE, echo=FALSE}
LancasterPharmacy <- read_csv('LancasterPharmacy.csv')

LancasterPharmacy <- LancasterPharmacy%>%
  mutate(Pharmacy = str_extract(LancasterPharmacy$`Organizations Name`, '.*#'))%>%
  select(Pharmacy, `Organizations Name`, Address, Hours, `Vaccine Type`, `Phone #`)

LancasterPharmacy$Pharmacy <- sub(' #', '', LancasterPharmacy$Pharmacy)
```

```{r Lancaster Pharmacy Geo, warning=FALSE, message=FALSE, echo=FALSE}
for (i in 1:nrow(LancasterPharmacy)){

  result <- geocode(LancasterPharmacy$Address[i], output = 'latlona', source = 'google')
  
  LancasterPharmacy$lon[i] <- as.numeric(result[1])
  LancasterPharmacy$lat[i] <- as.numeric(result[2])
  LancasterPharmacy$geoAddress[i] <- as.character(result[3])
}

write.csv(LancasterPharmacy, 'LancasterPharmacyGeo.csv')
```

```{r Compton Mobile & Pharm & Lan Pharm, warning=FALSE, message=FALSE, echo=FALSE, include=FALSE}
leaflet(ComptonMobile)%>%
  addTiles()%>%
  addMarkers(~lon, ~lat, label = ~as.character(`Name of Facility`))%>%
  addMarkers(~lon, ~lat, label = ~as.character(Name), data = ComptonPharmacy)%>%
  addMarkers(~lon, ~lat, label = ~as.character(`Organizations Name`), data = LancasterPharmacy)
```

```{r Palmdale Pharmacy, message=FALSE, warning=FALSE, echo=FALSE}
PalmdalePharmacy <- read_csv('PalmdalePharmacy.csv')

PalmdalePharmacy <- PalmdalePharmacy%>%
  mutate(Pharmacy = str_extract(PalmdalePharmacy$`Organizations Name`, '.*#'))%>%
  select(Pharmacy, `Organizations Name`, Address, Hours, `Vaccine Type`, `Phone #`)

PalmdalePharmacy$Pharmacy <- sub(' #', '', PalmdalePharmacy$Pharmacy)
```

```{r Palmdale Pharmacy Geo, warning=FALSE, message=FALSE, echo=FALSE}
for (i in 1:nrow(PalmdalePharmacy)){

  result <- geocode(PalmdalePharmacy$Address[i], output = 'latlona', source = 'google')
  
  PalmdalePharmacy$lon[i] <- as.numeric(result[1])
  PalmdalePharmacy$lat[i] <- as.numeric(result[2])
  PalmdalePharmacy$geoAddress[i] <- as.character(result[3])
}

write.csv(PalmdalePharmacy, 'PalmdalePharmacyGeo.csv')
```

```{r Compton Mobile & Pharm & Lan Pharm & Palm Pharm, warning=FALSE, message=FALSE, echo=FALSE, include=FALSE}
leaflet(ComptonMobile)%>%
  addTiles()%>%
  addMarkers(~lon, ~lat, label = ~as.character(`Name of Facility`))%>%
  addMarkers(~lon, ~lat, label = ~as.character(Name), data = ComptonPharmacy)%>%
  addMarkers(~lon, ~lat, label = ~as.character(`Organizations Name`), data = LancasterPharmacy)%>%
  addMarkers(~lon, ~lat, label = ~as.character(`Organizations Name`), data = PalmdalePharmacy)

```

```{r Santa Clarita Pharmacy, message=FALSE, warning=FALSE, echo=FALSE}
SantaClaritaPharmacy <- read_csv('SantaClaritaPharmacy.csv')

SantaClaritaPharmacy <- SantaClaritaPharmacy%>%
  mutate(Pharmacy = str_extract(SantaClaritaPharmacy$`Organizations Name`, '.*#'))%>%
  select(Pharmacy, `Organizations Name`, Address, Hours, `Vaccine Type`, `Phone #`)

SantaClaritaPharmacy$Pharmacy <- sub(' #', '', SantaClaritaPharmacy$Pharmacy)
```

```{r Santa Clarita Pharmacy Geo, warning=FALSE, message=FALSE, echo=FALSE}
for (i in 1:nrow(SantaClaritaPharmacy)){

  result <- geocode(SantaClaritaPharmacy$Address[i], output = 'latlona', source = 'google')
  
  SantaClaritaPharmacy$lon[i] <- as.numeric(result[1])
  SantaClaritaPharmacy$lat[i] <- as.numeric(result[2])
  SantaClaritaPharmacy$geoAddress[i] <- as.character(result[3])
}

write.csv(SantaClaritaPharmacy, 'SantaClaritaPharmacyGeo.csv')
```

```{r Compton Mobile & Pharm & Lan Pharm & Palm Pharm & SC Pharm, warning=FALSE, message=FALSE, echo=FALSE, fig.width=10, fig.height=6}
leaflet(ComptonMobile)%>%
  addTiles()%>%
  addMarkers(~lon, ~lat, label = ~as.character(`Name of Facility`))%>%
  addMarkers(~lon, ~lat, label = ~as.character(Name), data = ComptonPharmacy)%>%
  addMarkers(~lon, ~lat, label = ~as.character(`Organizations Name`), data = LancasterPharmacy)%>%
  addMarkers(~lon, ~lat, label = ~as.character(`Organizations Name`), data = PalmdalePharmacy)%>%
  addMarkers(~lon, ~lat, label = ~as.character(`Organizations Name`), data = SantaClaritaPharmacy)


```

<br>

Spatial visualization of the `FBO` and `CBO` sites geocoded that are providing vaccinations in the Compton, Santa Clarita, Palmdale, and Lancaster locations. Hovering over the **blue** markers displays the vaccination sites name.

```{r Pharm Merge, warning=FALSE, message=FALSE, echo=FALSE}
ComptonMobile <- ComptonMobile%>%
  rename('Organizations Name' = `Name of Facility`,
         'Vaccine Type' = Type,
         'Phone #' = `Contact Name`)

ComptonPharmacy <- ComptonPharmacy%>%
  rename('Organizations Name' = Name,
         'Vaccine Type' = `Type of Vaccine`,
         'Phone #' = `Contact Number`)

#str_extract(LancasterPharmacy$geoAddress, '(?<=,\\s).*(?=,\\sca)')

ComptonMobile <- ComptonMobile%>%
  mutate(City = rep('Compton', nrow(ComptonMobile)),
         Pharmacy = rep(NA, nrow(ComptonMobile)))%>%
  select(Pharmacy, `Organizations Name`, Address, City, `Vaccine Type`, `Phone #`, lon, lat,
         geoAddress)

ComptonPharmacy <- ComptonPharmacy%>%
  mutate(City = rep('Compton', nrow(ComptonPharmacy)))%>%
  select(Pharmacy, `Organizations Name`, Address, City, `Vaccine Type`, `Phone #`, lon, lat,
         geoAddress)
LancasterPharmacy <- LancasterPharmacy%>%
  mutate(City = rep('Lancaster', nrow(LancasterPharmacy)))%>%
  select(Pharmacy, `Organizations Name`, Address, City, `Vaccine Type`, `Phone #`, lon, lat,
         geoAddress)
PalmdalePharmacy <- PalmdalePharmacy%>%
  mutate(City = rep('Palmdale', nrow(PalmdalePharmacy)))%>%
  select(Pharmacy, `Organizations Name`, Address, City, `Vaccine Type`, `Phone #`, lon, lat,
         geoAddress)
SantaClaritaPharmacy <- SantaClaritaPharmacy%>%
  mutate(City = rep('Santa Clarita', nrow(SantaClaritaPharmacy)))%>%
  select(Pharmacy, `Organizations Name`, Address, City, `Vaccine Type`, `Phone #`, lon, lat,
         geoAddress)

PharmMerge <- rbind(ComptonMobile, ComptonPharmacy, LancasterPharmacy, PalmdalePharmacy,
                    SantaClaritaPharmacy)
PharmMerge <- PharmMerge%>%
  filter(!is.na(PharmMerge$Pharmacy))

PharmMerge$Pharmacy <- sub('RiteAid', 'Rite Aid', PharmMerge$Pharmacy)

PharmMerge$Pharmacy <- factor(PharmMerge$Pharmacy)
```

```{r Pharm Only, warning=FALSE, message=FALSE, echo=FALSE, fig.width=10, fig.height=6}
# PharmIcons <- iconList(CVS = makeIcon("C:/Users/Brandyn Ruiz/OneDrive - University of Southern California/CDU/ClubsClinics/CVS.png", 18, 18),
#                        Walmart = makeIcon("C:/Users/Brandyn Ruiz/OneDrive - University of Southern California/CDU/ClubsClinics/Walmart.png", 18, 18),
#                        `Rite Aid` = makeIcon("C:/Users/Brandyn Ruiz/OneDrive - University of Southern California/CDU/ClubsClinics/RiteAid.png", 18, 18),
#                        Albertsons = makeIcon("C:/Users/Brandyn Ruiz/OneDrive - University of Southern California/CDU/ClubsClinics/Albertsons.png", 18, 18),
#                        Costco = makeIcon("C:/Users/Brandyn Ruiz/OneDrive - University of Southern California/CDU/ClubsClinics/Costco.png", 18, 18),
#                        Walgreens = makeIcon("C:/Users/Brandyn Ruiz/OneDrive - University of Southern California/CDU/ClubsClinics/Walgreens.png", 18, 18),
#                        Vons = makeIcon("C:/Users/Brandyn Ruiz/OneDrive - University of Southern California/CDU/ClubsClinics/Vons.png", 18, 18),
#                        Ralphs = makeIcon("C:/Users/Brandyn Ruiz/OneDrive - University of Southern California/CDU/ClubsClinics/Ralphs.png"))

Hour24 <- read_csv("C:/Users/Brandyn Ruiz/OneDrive - University of Southern California/CDU/Compton/24HourGeocode.csv")

icons <- awesomeIcons(
  icon = 'ios-close',
  iconColor = 'black',
  library = 'ion',
  markerColor = 'orange')

leaflet(PharmMerge)%>%
  addTiles()%>%
  #addMarkers(~lon, ~lat, label = ~as.character(`Organizations Name`), icon = ~PharmIcons[Pharmacy])
  addMarkers(~lon, ~lat, label = ~as.character(`Organizations Name`), 
             icon = list(iconUrl = "C:/Users/Brandyn Ruiz/OneDrive - University of Southern California/CDU/ClubsClinics/CVS.png",
                         iconSize = c(80, 80)), data = PharmMerge%>%filter(Pharmacy == 'CVS'))%>%
  addMarkers(~lon, ~lat, label = ~as.character(`Organizations Name`), 
             icon = list(iconUrl = "C:/Users/Brandyn Ruiz/OneDrive - University of Southern California/CDU/ClubsClinics/Walmart.png",
                         iconSize = c(100, 100)), data = PharmMerge%>%
               filter(Pharmacy == 'Walmart'))%>%
  addMarkers(~lon, ~lat, label = ~as.character(`Organizations Name`), 
             icon = list(iconUrl = "C:/Users/Brandyn Ruiz/OneDrive - University of Southern California/CDU/ClubsClinics/RiteAid.png",
                         iconSize = c(140, 140)), data = PharmMerge%>%
               filter(Pharmacy == 'Rite Aid'))%>%
  addMarkers(~lon, ~lat, label = ~as.character(`Organizations Name`), 
             icon = list(iconUrl = "C:/Users/Brandyn Ruiz/OneDrive - University of Southern California/CDU/ClubsClinics/Albertsons.png",
                         iconSize = c(80, 80)), data = PharmMerge%>%
               filter(Pharmacy == 'Albertsons'))%>%
  addMarkers(~lon, ~lat, label = ~as.character(`Organizations Name`), 
             icon = list(iconUrl = "C:/Users/Brandyn Ruiz/OneDrive - University of Southern California/CDU/ClubsClinics/Costco.png",
                         iconSize = c(80, 80)), data = PharmMerge%>%
               filter(Pharmacy == 'Costco'))%>%
  addMarkers(~lon, ~lat, label = ~as.character(`Organizations Name`), 
             icon = list(iconUrl = "C:/Users/Brandyn Ruiz/OneDrive - University of Southern California/CDU/ClubsClinics/Walgreens.png",
                         iconSize = c(60, 60)), data = PharmMerge%>%
               filter(Pharmacy == 'Walgreens'))%>%
  addMarkers(~lon, ~lat, label = ~as.character(`Organizations Name`), 
             icon = list(iconUrl = "C:/Users/Brandyn Ruiz/OneDrive - University of Southern California/CDU/ClubsClinics/Vons.png",
                         iconSize = c(140, 140)), data = PharmMerge%>%
               filter(Pharmacy == 'Vons'))%>%
  addMarkers(~lon, ~lat, label = ~as.character(`Organizations Name`), 
             icon = list(iconUrl = "C:/Users/Brandyn Ruiz/OneDrive - University of Southern California/CDU/ClubsClinics/Ralphs.png",
                         iconSize = c(80, 80)), data = PharmMerge%>%
               filter(Pharmacy == 'Ralphs'))%>%
  addMarkers(~lon, ~lat, label = ~as.character(`Organizations Name`), data = ComptonMobile%>%
               filter(is.na(Pharmacy)))%>%
  addMarkers(~lon, ~lat, label = ~as.character(`Organizations Name`), data = ComptonPharmacy%>%
               filter(is.na(Pharmacy)))%>%
  addMarkers(~lon, ~lat, label = ~as.character(`Organizations Name`), data = LancasterPharmacy%>%
               filter(is.na(Pharmacy)))%>%
  addMarkers(~lon, ~lat, label = ~as.character(`Organizations Name`), data = PalmdalePharmacy%>%
               filter(is.na(Pharmacy)))%>%
  addMarkers(~lon, ~lat, label = ~as.character(`Organizations Name`), data = SantaClaritaPharmacy%>%
               filter(is.na(Pharmacy)))%>%
  addAwesomeMarkers(~lon, ~lat, icon = icons, label=~as.character(Club), data = Hour24)%>%
  addCircles(~lon, ~lat, radius = 804, color = 'black', fillColor = 'green', opacity = 0.5,
             data = Hour24)%>%
  addMeasure(position = 'bottomleft',
             primaryLengthUnit = 'miles',
             primaryAreaUnit = 'sqmiles',
             activeColor = '#3D535D',
             completedColor = '#7D4479',
             localization = 'en')
  
```

<br>

The **blue** markers are `FBO` and `CBO` vaccination sites and the `pharmacy sites` are with their respective icons. The **Orange** markers map the locations of the 24 Hour Fitness Centers and `CBO` in the given proximity of a half-mile radius marked in the **green** circles. The distance measured on the bottom left will measure the distance in miles from two points. Select an **orange** marker to a `pharmacy site` icon or a `CBO` icon providing vaccinations.

### List of 24 Hour Fitness Centers and CBOs
```{r 24 Hour Table, warning=FALSE, message=FALSE, echo=FALSE}
Table24 <- Hour24%>%
  select(Club, Address)

Table24%>%
  kbl(caption = "List of Mobile Sites")%>%
#  kable_classic(full_width = T, html_font = 'Cambria')
  kable_styling(full_width = F, html_font = 'Cambria', bootstrap_options = c('striped', 'hover'))

```

<br>

Here is the original listing of `24 Hour Fitness` centers and other `CBO` provided by Dr. Vargas that represent the **orange** markers.


```{r Half-Mile Table, warning=FALSE, message=FALSE, echo=FALSE, include=FALSE}
# book1 <- read_csv('Book1.csv')
# 
# book1%>%
#   kbl(caption = "List of Site Within Half-Mile")%>%
# #  kable_classic(full_width = T, html_font = 'Cambria')
#   kable_styling(full_width = F, html_font = 'Cambria', bootstrap_options = c('striped', 'hover'))

```